DOpElib - Deal Optimization Environment

### 2012-06-19 Examples/PDE/StatPDE/Example9/content.tex
Modifications in the program to allow evaluation of residual type error estimators, like the one for L2 and H1 error. To allow that this can be done in the same framework as the dwr-estimator there is a new method ResidualModifier in the PDEs. This should always be applied to the terms residual and jump terms in Strong...Residual. It is modified by the error estimators to switch between the calculation of the integral over the residual and the norm of the residual. PDE/StatPDE/Example9 has been modified to calculate these new values in addition to the dwr estimates.

>>>>

Note that in the above three functions we always apply the method \texttt{ResidualModifier} both to the 
residual as well as to the jumps on the faces. This is done to assert that we can apply both a 
DWR-error estimator where the residual should be multiplied with the computed weights (then this function 
does not do anything) as well as Residual Type error estimator for the $L^2$ or $H^1$ norm where we need to calculate element wise norms of the residual and the jumps. Then this function calculates the appropriate 
local terms, e.g., the square of the residual scaled with appropriate powers of the local mesh size.
